Imputation of Incomplete Multilevel Data with R

### 2024-01-10 Manuscript/manuscript.qmd
Updated manuscript
I have removed the 'no pmm' part from the Heckman model. Additionally, I've included the plot function with echo=FALSE, making it suitable for copying and pasting into the appendix later on. However, the pattern function with cluster still does not work. Regarding the box 3 about the prediction matrix, previously i have added relevant information about this (with an equation) in the Imputation flow. Please review this information to ensure that the box is constructed appropriately, avoiding redundant information throughout the paper. Thanks.

The popular [mice]{.pkg} package in [R]{.proglang} @R

### scope

@@

### concepts in multilevel data

Many datasets include individuals that are clustered together, for example in geographic regions, or even different studies. In the simplest case, individuals (e.g., students) are nested within a single cluster (e.g., school classes). More complex clustered structures may occur when there are multiple hierarchical levels (e.g., students in different schools or patients within hospitals within regions across countries), or when the clustering is non-nested (e.g., electronic health record data from diverse settings and populations within large databases). With clustered data we generally assume that individuals from the same cluster tend to be more similar than individuals from other clusters. In statistical terms, this implies that observations from the same cluster are not independent and may in fact be correlated. If this correlation is left unaddressed, estimates of *p* values, confidence intervals even model parameters are prone to bias  [@loca01]. Statistical methods for clustered data typically adopt hierarchical models that explicitly describe the grouping of observations. These models are also known as 'multilevel models', 'hierarchical models', 'mixed effect models', 'random effect models', and in the context of time-to-event data as 'frailty models'. Table \ref{tab:clus} provides an overview of some key concepts in multilevel modeling.

::: callout
Box 1. The intraclass correlation coefficient. 
:::

```{R}
#| echo: false
# concepts |>
#   kable(
#     booktabs = T,
#     escape = F,
#     caption = "Concepts in multilevel methods",
#     col.names = c("Concept", "Details"),
#     align = "l"
#   ) |>
#   column_spec(c(1), width = "3cm") |>
#   column_spec(c(2), width = "12cm")
```

In [R]{.proglang}, multilevel models may be fitted using the package [lme4]{.pkg}. For linear mixed-effects models, the function

@@

### concepts in missing data

@@

### imputation with mice

@@

::: callout
Box 3. The predictor matrix. The entries corresponding to the level-1 predictors are coded with a 3, indicating that both the original values as well as the cluster means of the predictor are included into the imputation model. The entry of 4 in the predictor matrix adds three variables to the imputation model for the imputation model predictor: the value of the predictor, the cluster means of the predictor and the random slopes of the predictor.
- -2 = cluster variable 
- 1 = overall effect
- 3 = overall + group-level effect 
- 4 = individual-level (random) and group-level (fixed) effect 
:::

@@

There are different strategies that can be adopted in the imputation process that account for clustering: inclusion of cluster indicator variable, performing a separate imputation process for each cluster, or performing a simultaneous imputation process by using an imputation method that accounts for clustering.(Stata: https://www.stata.com/support/faqs/statistics/clustering-and-mi-impute/) TODO: replace ref.

@@

### Assess Estimation Procedure Robustness to Missing Data
Before diving into imputation, make sure your estimation model can handle missing data. Sometimes, simpler methods like complete case analysis might be suffice, especially if your missingness is low (usually <5%). There are scenarios in which specific Maximum Likelihood (ML) estimation methods outperform Multiple Imputation (MI) methods, for instance when the response variable is the sole incomplete variable, mixed models demonstrate robustness to missing data under the Missing at Random (MAR) assumption and with a correct variance-covariance specification.\cite{Molenberghs_2007}.

@@

The imputation model can incorporate additional terms compared to the main model without causing compatibility issues. For instance, it's recommended to include the outcome variable in the imputation model for prediction variables \cite{moons2006a}. In cases where the outcome is time-to-event, the Nelson-Aalen estimate of the time to the event should be added as a covariate in the imputation model [REF]. Additionally, including auxiliary variables, even if not part of the main model, can be linked to the probability of missingness, improving the likelihood of meeting the Missing at Random (MAR) assumption and enhancing estimation efficiency \cite{hardt2012a}.

@@

Recipes have been proposed for imputing incomplete level-1 and level-2 variables for hierarchical models \cite{buuren2018a} ($\S$ 7.10), which can be convenient to follow when dealing with numerous variables (interaction terms at different levels) and models with many random effects that are prone to convergency problems due to overspecification in the imputation model. These rules were designed to ensure compatibility among the conditionally specified imputation models and congeniality between the imputation and the main model. However, they may not be applicable to all 2l imputation methods; for instance, the 2l.2stage imputation methods of the micemd package only allow the inclusion of random predictor variables (2).

On the other hand, the formula option is useful in specifying complex imputation models with polynomial terms or interactions and compared with the prediction matrix method do not requires the inclusion of additional terms as Just Another Variable (JAV) \cite{buuren2018a}($\S$ 6.4).

@@

While the majority of Multiple Imputation by Chained Equations (MICE) methods are based on Missing at Random (MAR) assumptions, field expert input may suggest that the Missing Not at Random (MNAR) mechanism could be plausible for certain variables. An MNAR variable is one in which the probability of missingness depends on an unobservable variable. This can occur when missingness is associated with the incomplete value itself (self-marking) or when there is an unobserved variable linked to both the value and the probability of missingness of the incomplete value (indirectly non-informative). Specifically, for the indirectly non-informative case in hierarchical datasets, imputation methods based on the Heckman method can be considered.\cite{hammon2020,hammon2022,munoz2023}

@@

### obesity data

@@

```{r}
#| prompt: true
Nulmodel <- lmer(BMI ~ 1 + (1|Cluster), data = Obesity)
# performance::icc(Nulmodel)
```

@@

It suggests using '2l.2stage.bin' for the FAV variable and '2l.2stage.norm' for the age variable. However, after inspecting the age density plot, we consider modifying its method to
'2l.2stage.pmm'. For the BMI variable, we employ deterministic imputation.

```{r obesitymeth, eval=TRUE}
meth_mar <-
  find.defaultMethod(
    Obesity,
    ind.clust = 1,
    I.small = 7,
    ni.small = 100,
    prop.small = 0.4
  )
meth_mar["BMI"] <- "~ I(Weight / (Height)^2)"
meth_mar["Age"] <- "2l.2stage.pmm"
```

For these imputation models, it is necessary to specify the prediction matrix, with the cluster
variable labelled as -2 and the predictor variable measured within clusters labelled as 2, encompassing all variables. We need to suprime the variable Time as this variable is not specified in the main model. We also  modify the relationship between BMI, weight and height in the prediction matrix to avoid circular predictions. Then we proceed to run the imputation model.
```{r obesity-predmar,out.width="70%", eval=TRUE}
pred_mar <- quickpred(Obesity)
pred_mar[, "Cluster"] <- -2 
pred_mar[, "Time"] <- 0
pred_mar[pred_mar == 1] <- 2
pred_mar[c("Height", "Weight"), "BMI"] <- 0
plot_pred(pred_mar)
imp_mar <-
  mice(
    data = Obesity,
    method = meth_mar,
    predictorMatrix = pred_mar,
    printFlag = FALSE
  )
```

```{r obesity-predmar1,eval=TRUE}
summary(complete(imp_mar,"long")$Weight)
```
We are also contemplating the utilisation of the predictive mean matching (pmm) option, as the values imputed using a fully parametric method may be implausibly low for some patients.

```{r obesity-predmar_pmm, eval=TRUE}
meth_mar["Weight"] <- "2l.2stage.pmm"
imp_mar_pmm <- mice(
  data = Obesity,
  method = meth_mar,
  predictorMatrix = pred_mar,
  printFlag = FALSE
)
```

```{r obesity-predmar_pmm1,eval=TRUE}
summary(complete(imp_mar_pmm, "long")$Weight)
plot_trace(imp_mar_pmm, "Weight")
ggmice(imp_mar_pmm, aes(.imp, Weight)) + 
  geom_jitter()
```

Analyze the imputed data.
```{R}
#| prompt: true
#| warning: false
# fit <- with(
#     imp_mar_pmm,
#     lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age | Cluster)
#     )
fit <- with(
    imp_mar_pmm,
    lmer(BMI ~ Age + FamOb + Gender + (1 + Age | Cluster))
    )
est <- testEstimates(as.mitml.result(fit), extra.pars = TRUE)
```

@@

These two equations are jointly estimated under the assumption that the error terms are interconnected with a bivariate normal distribution. For a more comprehensive understanding of the model and the exclusion restriction, see \cite{munoz2023a}.

@@

```{r obesity-predmnar1, eval=TRUE}
meth_mnar <- meth_mar
meth_mnar["Weight"] <- "2l.2stage.heckman"
```
Then we proceed to run the imputation model as before, after executing these imputation procedures, it is essential to assess convergence and the coherence of the imputed values.
```{r obesity-predmnar2,eval=TRUE}
imp_mnar <- mice(
  data = Obesity,
  method = meth_mnar,
  predictorMatrix = pred_mnar,
  printFlag = FALSE
)
summary(complete(imp_mnar, "long")$Weight)
```

Upon examining the weight variable, we noticed that the imputed range falls outside the realm of plausible values (as weight should be positive).

```{r obesity-predmnar3,eval=TRUE}
summary(complete(imp_mnar, "long")$Weight)
```
Consequently, as before we  use the 'pmm', option but this time for the Heckman imputation, this approach ensures that the imputed values remain within the range of observable values. We then run the imputation model but this time using the option of pmm, to assure that weight values are in the range of the observable data, this can be implemented by setting the pmm parameter to true.

```{r obesity-predmnarp, eval=TRUE}
imp_mnar_pmm <-
  mice(
    data = Obesity,
    method = meth_mnar,
    predictorMatrix = pred_mnar,
    pmm = T,
    printFlag = FALSE
  )
```

We check the convergence of the results
```{r obesity-predmnarp1, eval=TRUE}
summary(complete(imp_mnar_pmm, "long")$Weight)
plot_trace(imp_mar_pmm, "Weight")
```

After this modification we proceed to compare the effects on the model. We
run the analysis model on each of the completed datasets as well as the dataset where the
incomplete values are removed (Complete Case analysis, CC).

```{r models, eval=TRUE}
# cc_rs <- with(setDT(Obesity)[complete.cases(Obesity), ],
#               lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age |
#                     Cluster))
mar_rs <- with(
  imp_mar, 
  lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age | Cluster)
  )
mar_pmm_rs <- with(
    imp_mar_pmm,
    lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age | Cluster)
    )
mnar_rs <- with(
  imp_mnar, 
  lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age | Cluster)
  )
mnar_pmm_rs <- with(
  imp_mnar_pmm,
  lme(BMI ~ Age + FamOb + Gender, random =  ~ 1 + Age | Cluster)
  )
# list_models <- list(cc_rs, mar_rs, mar_pmm_rs, mnar_rs, mnar_pmm_rs)
# plot_models(list_models,
#             mod_name = c("Complete case", "MAR", "MAR_pmm", "MNAR", "MNAR_pmm"))
```

```{r}
est <- testEstimates(as.mitml.result(mnar_pmm_rs), extra.pars = TRUE)
```

```{r}
#| prompt: true
est$extra.pars |> 
  round(3) |>
  kable()
```
We note that there is minimal disparity in the age effect, FamObs, or  Gender across the various imputation models under consideration. An analysis of the intercept reveals that, under the MNAR assumption, a higher average BMI is anticipated compared to the MAR assumption.
Nonetheless, with respect to precision of estimates, we notice that in general MNAR imputation leads to wider confidence intervals, in this case it does not have any influence on the final result but there could be cases where variation in the assumed missing mechanism could lead also to differences on significant test and therefore lead to contradictory conclusions.

>>>>

The popular [mice]{.pkg} package in [R]{.proglang} @R
TODO: @Hanne(Is this section relevant?)

### Scope

@@

### Concepts in multilevel data

Many datasets include individuals that are clustered together, for example in geographic regions, or even different studies. In the simplest case, individuals (e.g., students) are nested within a single cluster (e.g., school classes). More complex clustered structures may occur when there are multiple hierarchical levels (e.g., students in different schools or patients within hospitals within regions across countries), or when the clustering is non-nested (e.g., electronic health record data from diverse settings and populations within large databases). With clustered data we generally assume that individuals from the same cluster tend to be more similar than individuals from other clusters. In statistical terms, this implies that observations from the same cluster are not independent and may in fact be correlated. If this correlation is left unaddressed, estimates of *p* values, confidence intervals even model parameters are prone to bias  [@loca01]. Statistical methods for clustered data typically adopt hierarchical models that explicitly describe the grouping of observations. These models are also known as 'multilevel models', 'hierarchical models', 'mixed effect models', 'random effect models', and in the context of time-to-event data as 'frailty models'. Table \ref{tab:clus0} provides an overview of some key concepts in multilevel modeling.

```{r clus0,  echo = FALSE, warning = FALSE,cache = TRUE}
concepts <- data.frame(Concept=c("Sample units","Cluster","Hierarchical data","Level-1","Level-2","Hierarchical model","Fixed effect","Random effect","Mixed effect","ICC","Stratified intercept"),
                       Details=c("Units of the population from which measurements are taken in a sample, e.g., students.", "Variable that specify the cluster or agruppation, e.g., Classroom","Data are grouped into clusters at different levels, observations belonging to the same cluster are expected to share certain characteristics.","Variable that varies within a cluster, eg. Test score","Variable that does not vary within a cluster but between, e.g. teacher experience.","Model accounting for dependant observations relying on certain parameters ( within cluster) which in turn depend on other parameters (between cluster)" ,"Effects that are constant across all sample units, e.g. something that researchers control for and can repeat, such as  a teaching strategy (tutoring after class)","Effects that are a source of random variation in the data, and whose levels are not fully sampled. e.g. test score tendency during academic year between students due to no controlled factors such as  genetic,family history","Includes fixed and random effects, e.g. the fixed effect would be the treatment effect of a drug and the random effect would be the ID of the hospital where the patient is treated. Multilevel models typically accommodate for variability by including a separate group mean for each cluster e.g random intercept on hospitals. In addition to random intercepts, multilevel models can also include random coefficients and heterogeneous residual error variances across clusters (see e.g. @gelm06, @hox17 and @jong21).","The variability due to clustering is often measured by means of the intraclass coefficient (ICC). The ICC can be seen as the percentage
of variance that can be attributed to the cluster-level, where a high ICC would indicate that a lot of variability is due to the cluster structure.",
                                 ""))
library(kableExtra)
concepts%>%
  kable( booktabs = T, escape = F,
         caption = "Concepts in multilevel methods",
         col.names = c("Concept","Details"), align = "l")%>%
  column_spec(c(1), width = "3cm")%>%
  column_spec(c(2), width = "12cm")
```

In [R]{.proglang}, multilevel models may be fitted using package such as  [lme4]{.pkg} or [nlme]{.pkg}. For linear mixed-effects models, the function

@@

### Concepts in missing data

@@

Table 2: Concepts in missing data methods

| **Concept**    | **Details**                                                                |
|----------------|----------------------------------------------------------------------------|
| MCAR           | Missing Completely At Random, where the probability to be missing is equal |
|                | across all data entries                                                    |
| MAR            | Missing At Random, where the probability to be missing depends on observed |
|                | information                                                                |
| MNAR           | Missing Not At Random (MNAR), where the probability to be missing          |
|                | depends on unrecorded information, making the missingness non-ignorable    |
|                | [@rubi76; @meng94].                                                        |
|                |                              |

### Imputation with mice

@@

::: callout
TODO: @ Hanne i added a wide explanation about hte prediction matrix in the Model Specification subsection, so you can check it and consider to modify your box.. because i dont think is usefull to repeat information across the paper...

Box 3. The predictor matrix. The entries corresponding to the level-1 predictors are coded with a 3, indicating that both the original values as well as the cluster means of the predictor are included into the imputation model. The entry of 4 in the predictor matrix adds three variables to the imputation model for the imputation model predictor: the value of the predictor, the cluster means of the predictor and the random slopes of the predictor.
- -2 = cluster variable 
- 1 = overall effect
- 3 = overall + group-level effect 
- 4 = individual-level (random) and group-level (fixed) effect 
:::

@@

There are different strategies that can be adopted in the imputation process that account for clustering: inclusion of cluster indicator variable, performing a separate imputation process for each cluster, or performing a simultaneous imputation process by using an imputation method that accounts for clustering.\cite{zotero-516}

@@

### Assess Estimation Procedure Robustness to Missing Data
Before diving into imputation, make sure your estimation model can handle missing data. Sometimes, simpler methods like complete case analysis might be suffice, especially if your missingness is low (usually <5%). There are scenarios in which specific Maximum Likelihood (ML) estimation methods outperform Multiple Imputation (MI) methods, for instance when the response variable is the sole incomplete variable, mixed models demonstrate robustness to missing data under the Missing at Random (MAR) assumption and with a correct variance-covariance specification.\cite{molenberghs2007}.

@@

The imputation model can incorporate additional terms compared to the main model without causing compatibility issues. For instance, it's recommended to include the outcome variable in the imputation model for prediction variables \cite{moons2006}. In cases where the outcome is time-to-event, the Nelson-Aalen estimate of the time to the event should be added as a covariate in the imputation model [REF]. Additionally, including auxiliary variables, even if not part of the main model, can be linked to the probability of missingness, improving the likelihood of meeting the Missing at Random (MAR) assumption and enhancing estimation efficiency \cite{hardt2012}.

@@

Recipes have been proposed for imputing incomplete level-1 and level-2 variables for hierarchical models \cite{buur18} ($\S$ 7.10), which can be convenient to follow when dealing with numerous variables (interaction terms at different levels) and models with many random effects that are prone to convergency problems due to overspecification in the imputation model. These rules were designed to ensure compatibility among the conditionally specified imputation models and congeniality between the imputation and the main model. However, they may not be applicable to all 2l imputation methods; for instance, the 2l.2stage imputation methods of the micemd package only allow the inclusion of random predictor variables (2).

On the other hand, the formula option is useful in specifying complex imputation models with polynomial terms or interactions and compared with the prediction matrix method do not requires the inclusion of additional terms as Just Another Variable (JAV) \cite{buur18}($\S$ 6.4).

@@

While the majority of Multiple Imputation by Chained Equations (MICE) methods are based on Missing at Random (MAR) assumptions, field expert input may suggest that the Missing Not at Random (MNAR) mechanism could be plausible for certain variables. An MNAR variable is one in which the probability of missingness depends on an unobservable variable. This can occur when missingness is associated with the incomplete value itself (self-marking) or when there is an unobserved variable linked to both the value and the probability of missingness of the incomplete value (indirectly non-informative). Specifically, for the indirectly non-informative case in hierarchical datasets, imputation methods based on the Heckman method can be considered.\cite{hammon2020,hammon2022,munoz2023b}

@@

### Obesity data

@@

```{r}
#| prompt: true
Nulmodel <- lme4::lmer(BMI ~ 1 + (1|Cluster), data = Obesity)
performance::icc(Nulmodel)
```

@@

It suggests using '2l.2stage.bin' for the FAV variable and '2l.2stage.norm' for the age variable. However, after inspecting the age and weight density plot, we consider modifying its method to
'2l.2stage.pmm'. For the BMI variable, we employ deterministic imputation.

```{r obesitymeth, eval=TRUE}
meth_mar <-
  find.defaultMethod(
    Obesity,
    ind.clust = 1,
    I.small = 7,
    ni.small = 100,
    prop.small = 0.4
  )
meth_mar["BMI"] <- "~ I(Weight / (Height)^2)"
meth_mar["Age"] <- "2l.2stage.pmm"
meth_mar["Weight"] <- "2l.2stage.pmm"

```

For these imputation models, it is necessary to specify the prediction matrix, with the cluster
variable labelled as -2 and the predictor variable measured within clusters labelled as 2, encompassing all variables. We need to suprime the variable Time as this variable is not specified in the main model. We also  modify the relationship between BMI, weight and height in the prediction matrix to avoid circular predictions. Then we proceed to run the imputation model.
```{r obesity-predmar,out.width="70%", eval=TRUE}
pred_mar <- quickpred(Obesity)
pred_mar["Weight",] <- 2
pred_mar["Weight","Weight"] <- 0
pred_mar[, "Cluster"] <- -2 
pred_mar[, "Time"] <- 0
pred_mar[pred_mar == 1] <- 2

pred_mar[c("Height", "Weight"), "BMI"] <- 0
#plot_pred(pred_mar)
imp_mar <-
  mice(
    data = Obesity,
    method = meth_mar,
    predictorMatrix = pred_mar,
    printFlag = FALSE
  )
```

```{r obesity-predmar_pmm1,eval=TRUE}
summary(complete(imp_mar, "long")$Weight)
plot_trace(imp_mar, "Weight")
ggmice(imp_mar, aes(.imp, Weight)) + 
  geom_jitter()
```

@@

These two equations are jointly estimated under the assumption that the error terms are interconnected with a bivariate normal distribution. For a more comprehensive understanding of the model and the exclusion restriction, see \cite{munoz2023}.

@@

```{r obesity-predmnar1, eval=TRUE}
meth_mnar <- meth_mar
meth_mnar["Weight"] <- "2l.2stage.heckman"
```
As before we  use the 'pmm', option but this time for the Heckman imputation, this approach ensures that the imputed values remain within the range of observable values. We then run the MNAR imputation model by setting the pmm parameter to true.

```{r obesity-predmnarp, eval=TRUE}
imp_mnar <-
  mice(
    data = Obesity,
    method = meth_mnar,
    predictorMatrix = pred_mnar,
    pmm = T,
    printFlag = FALSE
  )
```

We check the convergence of the results
```{r obesity-predmnarp1, eval=TRUE}
summary(complete(imp_mnar, "long")$Weight)
plot_trace(imp_mar, "Weight")
```

We proceed to compare the effects on the model. We
run the analysis model on each of the completed datasets as well as the dataset where the
incomplete values are removed (Complete Case analysis, CC).
```{r plotfunction, eval=TRUE, echo=FALSE}
library(broom.mixed)
plot_models <- function(list_models, mod_name){
  mod_table<-NULL
  for(i in 1:length(list_models)){
    mod <- list_models[[i]]  
    if(class(mod)[[1]]=="mira"){
      mod_tab <-summary(pool(mod), conf.int = TRUE)[,c("term","estimate","2.5 %","97.5 %","p.value")]
    }else{
      sum_cc <- (summary(mod,conf.int = TRUE))
      mod_tab<-data.frame(nlme::intervals(mod, which = "fixed")$fixed)
      mod_tab$term<-rownames(mod_tab)
      mod_tab$pvalue<-sum_cc$tTable[,5]
      mod_tab <-mod_tab[,c("term","est.","lower","upper","pvalue")]
      rownames(mod_tab)<-NULL

    }
    colnames(mod_tab)<-c("Coefficient","Estimate","lower","upper","p.value")
    mod_tab$model<-mod_name[i]
    mod_table<-rbind(mod_table,mod_tab)
  }

  plot <-ggplot(mod_table, aes(x = Coefficient, y = Estimate, ymin = lower, ymax = upper, group=model, color=model)) + 
    geom_hline(yintercept=0,linetype="dashed",color="black",size=0.1)+
    geom_linerange( position = position_dodge(width = 0.8)) + 
    geom_pointrange(size=0.1, position = position_dodge(width = 0.8))+coord_flip()+
    theme_classic()+theme(legend.position = "bottom")+scale_color_viridis_d()
  return(plot)
}
```
We proceed to fit the mixed model by using the complete case database and the imputed datasets (MAR,MNAR), and we compare the estimates of each dataset by using a plot (the plot function can be found in the appendix).
```{r models, eval=TRUE,warning=FALSE,message=FALSE}
# Save all datasets in a list
list_data <- list(Obesity |> filter(complete.cases(Obesity)), # complete case
                  imp_mar, # imputed under mar
                  imp_mnar) # imputed under mnar

# Run mixed models on each dataset
list_models <- lapply(list_data, 
                   FUN = function(x) 
                     with(x,nlme::lme(BMI ~ Age + FamOb + Gender, 
                                      random =  ~ 1 + Age | Cluster)))
# Plot coefficients
plot_models(list_models,
             mod_name = c("Complete case", "MAR", "MNAR"))
```

We note that there is minimal disparity in the age effect, FamObs, or  Gender across the various imputation models under consideration. An analysis of the intercept reveals that, under the MNAR assumption, a higher average BMI is anticipated compared to the MAR assumption.
Nonetheless, with respect to precision of estimates, we notice that in general MNAR imputation leads to wider confidence intervals, in this case it does not have any influence on the final result but there could be cases where variation in the assumed missing mechanism could lead also to differences on significant test and therefore lead to contradictory conclusions.
